Mealtime conversations between parents and their 2-year-old children in five cultural contexts

### 2023-07-12 manuscript/paper.Rmd
update repo for revision

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "manuel_bohn@eva.mpg.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal Analysis
      - Visualization
      - Writing – original draft
      - Writing – review & editing
  - name          : "Wilson Filipe da Silva Vieira"
    affiliation   : "1"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Marta Giner Torréns"
    affiliation   : "2"
    role:
      - Investigation
      - Conceptualization
      - Methodology
      - Writing – review & editing
  - name          : "Joscha Kärtner"
    affiliation   : "2"
    role:
      - Investigation
      - Conceptualization
      - Methodology
      - Writing – review & editing
  - name          : "Shoji Itakura"
    affiliation   : "3"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Lilia Cavalcante"
    affiliation   : "4"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Daniel Haun"
    affiliation   : "1"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Moritz Köster"
    affiliation   : "5,*"
    role:
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing
  - name          : "Patricia Kanngiesser"
    affiliation   : "6,*"
    role:
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "2"
    institution   : "Department of Psychology, University of Münster, Münster, Germany"
  - id            : "3"
    institution   : "Doshisha University, Center for Baby Science, Kyoto, Japan"
  - id            : "4"
    institution   : "Department of Behavior Theory and Research, Federal University of Pará, Belém, Brazil"
  - id            : "5"
    institution   : "University of Regensburg, Institute of Psychology, Regensburg, Germany"
  - id            : "6"
    institution   : "University of Plymouth, School of Psychology, Plymouth, UK"
  - id            : "*"
    institution   : "joint senior author"

authornote: |
  This research was funded by a grant from Volkswagen Foundation (89611–2), awarded to P.K.. The data assessment in Kyoto was partly funded by a JSPS Fellowship to M.K.. We would like to thank all the research assistants who supported the data assessments and coding: Phileas Heim, Chisato Fukuda, Julia Ohlendorf, Marlene Abromeit. We are grateful to Luke Maurits for statistical advice. All data and analysis code can be found in the following repository: https://github.com/ccp-eva/mealtime.

abstract: |
  Children all over the world learn language, yet, the contexts in which they do so varies substantially. This variation needs to be systematically quantified to build robust and generalizable theories of language acquisition. We compared communicative interactions between parents and their two-year-old children (N = 99 families) during mealtime across five cultural settings (Brazil, Ecuador, Argentina, Germany, Japan) and coded the amount of talk and gestures as well as their conversational embedding (interlocutors, speech acts, themes). We found a comparable pattern of communicative interactions across cultural settings, which were attenuated in ways that likely reflect local norms and values. These results suggest that children encounter similarly structured communicative environments across diverse cultural contexts and will inform theories of language learning.

keywords          : "Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction"
wordcount         : "7960"

@@

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : yes

@@

Cultural norms and beliefs structure social interactions and communication. As a consequence, children learn language under very different circumstances. We studied communicative interactions between parents and their children in five diverse cultural contexts. We found a common, child-centered pattern of communication that was attenuated in line with local norms and values. This suggests that children can rely on similar information sources and learning processes across cultural contexts.

@@

In recent decades, research on language acquisition has focused, to a large extent, on variation in language input and, in particular, the number of words children hear in naturalistic settings. This line of work was sparked by the finding that children who receive more input -- especially speech directly addressing them -- have better language skills [@hart1995meaningful; @weisleder2013talking; @bang2022spanish; @huttenlocher1991early; @walker1994prediction; @shneidman2012language]. From a theoretical perspective, more language input increases children’s opportunities for learning word-meaning mappings and allows them to build a larger vocabulary [@mcmurray2012word; @kachergis2022toward; @jones2017diversity]. The introduction of daylong audio recording devices and automated coding algorithms has provided further momentum to this endeavor [@lavechin2020open; @greenwood2011assessing; @cristia2021thorough]. As a consequence, the quantity of direct language input plays a central role in theories and formal models of language learning [@swingley2018quantitative; @braginsky2019consistency; @goodman2008does; @kachergis2022toward].

However, like most of developmental psychology [@nielsen2017persistent; @amir2020cross], research on language acquisition has largely focused on affluent societies of the global north and, as a consequence, the resulting theoretical proposals may fail to generalize to other cultural contexts. As studies in a greater variety of cultural settings have begun to accumulate [@casillas2021early; @bergelson2019north; @bunce2020cross; @loukatou2021child; @cristia2019child; @altinkamics2014context; @choi2000caregiver; @tardif1997caregiver], they have revealed substantial cultural variation in how much direct input children receive [@cristia2022systematic; see also @sperry2019reexamining for variation within an English-speaking sample]. Yet, children still reach major milestones in language development at similar ages [@casillas2020early; @brown2014language]. These findings highlight that theories and models of language learning need to extend beyond quantity of input and also include learning processes that compensate for variation in input [@kachergis2022toward; @jones2017diversity; @meylan2022learning; @bang2022time; @casillas2022learning].

It has been suggested that these compensatory learning processes leverage structural features of social interactions in which language is used [@rogoff2003firsthand; @casillas2020early; @shneidman2012language; @shneidman2016child]. Pragmatic accounts of language learning offer an explanation for how children use contextual information [e.g., @bohn2019pervasive; @tomasello2009constructing]: Social interactions, especially routines, follow predictable patterns that make it easier for children to infer what speakers are communicating about [@lieven1994crosslinguistic; @de2022ten; @masek2021beyond]. For instance, @roy2015predicting found that words were more easily learned when they were primarily used in a distinct spatial and temporal context. Similarly, establishing common ground over the course of an interaction provides information about the speaker’s intention independent of the words that are being used [@bohn2018common; @bohn2021young]. For example, @bohn_le_peloquin_koymen_frank_2020 showed that children identify the referent of an ambiguous word by inferring the topic of an ongoing conversation [see also @akhtar2002relevance]. These findings help to explain why the amount of conversational turn-taking in parent-child interactions predicts child language outcomes [@romeo2018beyond; @donnelly2021longitudinal]. Turn-taking results in continuous, structured conversations that provide information-rich learning opportunities.

In order to assess whether children can use structural features to complement direct verbal input, it is crucial to compare communicative interactions between adults and children across cultural settings. However, to our knowledge, there are very few quantitative comparisons. While ethnographic descriptions offer important and rich insights into individual cultural settings [see e.g., @de2011language; @gaskins2006cultural], quantitative comparisons are essential for understanding gradual cultural differences [@koester2022parental; @broesch2021opportunities; @hewlett1998culture] and offer core input for theory building (see language input studies discussed earlier).

One of the challenges of cross-cultural work lies in selecting an appropriate context for comparing the structure of communicative interactions [@broesch2022roadmap]. Prior work has shown that the amount of language input children receive varies substantially across routine activities. For example, @soderstrom2013caregivers found that Canadian adults spoke most during book reading and structured playtime [see also @tamis2019routine]. Such activities, however, are very specific to industrialized societies and less frequent or absent in other cultural contexts. A cross-culturally recurrent, and hence particularly promising, context for cross-cultural research is mealtime: across societies, meals are social events that are structured by -- and used to transmit -- cultural norms, values and beliefs [@ochs2006cultural; @fjellstrom2004mealtime; @blum2012dinner; @koester2022parental]. Furthermore, mealtimes have been a fruitful context for studying caregiver-child communication, for example, in the U.S. [e.g., @beals1993explanatory; @beals1997sources; @snow2006mealtime].

@@

The goal of this study was to compare communicative interactions between parents and their children during mealtime across diverse cultural settings. We aimed for a naturalistic but comparable setup by a) asking families to record in their homes, b) recruiting families with a single -- usually the first -- child between 2 and 3 years of age and c) focusing on 10-minute-long episodes during which three family members (mother, father, one child) were present. Even though the constellation of two parents and one child might be less representative of the overall family demographics in some settings, it allowed us to directly quantify and compare communicative interactions. We obtained recordings from five different cultural settings, including families living in the Global South and North, as well as in urban and rural settings: the city of Buenos Aires, Argentina, small villages in the Apeú region, Brazil, small villages close to Cotacachi, Ecuador, the city of Münster, Germany, and the city of Kyoto, Japan.

We coded and analyzed the data along nine dimensions that focused on the quantity of talk and gestures as well as their conversational embedding (interlocutors, speech acts, themes). In a first step, we analyzed if and how these dimensions differed in the five cultural settings. In a second step, we asked whether some cultural settings are more similar to one another. The five cultural settings offer an interesting perspective on the factors influencing mealtime conversations. For example, communicative interaction patterns could cluster by country (five clusters; one cluster per country), or by language family and geographical region (three clusters; Argentina, Brazil, Ecuador vs. Germany vs. Japan) or by degree of urbanization (two clusters; urban: Argentina, Germany, Japan vs. rural: Brazil, Ecuador). Based on previous work, we expected less direct input to children in the rural contexts (Cristia, 2022) but -- given a lack of comparable previous work -- we had no specific predictions for variation in the structure of communicative interactions.

@@

The final sample consisted of `r sum(dem$n)` families from five cultural contexts. This included `r dem%>%filter(country == "Argentina")%>%pull(n)` families from the city of Buenos Aires, Argentina (urban setting), `r dem%>%filter(country == "Brazil")%>%pull(n)` families from villages in the Amazon region near Apeú, Brazil (rural setting), `r dem%>%filter(country == "Ecuador")%>%pull(n)` from villages near Cotacachi, Ecuador (rural setting), `r dem%>%filter(country == "Germany")%>%pull(n)` families from the city of Münster, Germany (urban setting) and `r dem%>%filter(country == "Japan")%>%pull(n)` families from the city of Kyoto, Japan (urban setting). For the recording sessions, all families comprised a father, a mother and a child aged between 2 years and 3 years, 2 months. Almost all children were the first child in the family. Some videos partly included additional children (n = 1 for Argentina, Brazil and Ecuador).

@@

Families lived in villages of around 50 - 300 families in the Amazon region near Apeú, approximately 1.5 hours east of Belém, the capital of the state of Pará. They were recruited with the help of a local public health office. The family language was Brazilian Portuguese. Compensation included small toys for children and a certificate of participation for parents. Most parents had completed secondary school (~12 years of schooling, mothers: 50%; fathers: 56%). Mothers worked mainly as housewives (83%) while fathers engaged in paid labor (100%). Some families engaged in traditional subsistence activities such as tapioca farming, livestock breeding, or acaí and fruit harvesting. In line with employment status, the majority of children were looked after by their mothers.

@@

Here we coded who produced the utterance. The speaker could either be `child`, `mother`, or `father`. All sections containing no speech were coded as `silence`.

@@

### Themes and rounds

Here we coded the conversational coherence of the different utterances. For that we defined `themes` as sequences of utterances that related to one another. This applies for example to sequences of questions and answers but also to sequences in which the content of an utterance is directly related to the content of the previous utterance. Please note that such themes were coded locally and were not the same as topics. For example, if father and child exchanged four utterances about the child’s day in the kindergarten this was coded as one theme. If the same topic (day at the kindergarten) came up later again, this was coded as a separate theme. Each utterance within a theme was counted as a `round` to capture the sequence and length of a theme. Thus, each utterance was assigned a number for the theme and a number for the round within theme. Themes could have interjections of one or two utterances. After more than two interjections we coded a new theme. For example, if father and child talked about food and the mother made an unrelated comment in between, the mother’s comment would be coded as a separate theme while the other theme continued around it:

Child: "I want more"	 			        (theme (t) 1, round (r) 1)

Father: "Do you want more soup?"		(t1, r2)

Mother: "Phew, I'm hot			        (t2, r1)

Child: "No, bread				            (t1, r3)

Father: "I'll get some"			        (t1, r4)

### Speech acts

Each utterance was coded as either being a `question`, `assertion` or `imperative`. Imperatives were only coded if the the utterance was grammatically structured as an imperative. For example "Pass me the salt!" was coded as an imperative while "You should give me the salt." was not.

@@

For each cultural setting, we selected 15% of videos and had them re-coded by a second coder (native speaker of the respective language). The second coder relied on the sequencing of the primary coder. Inter-rater reliability was generally very good. For recipient, the agreement between coders was `r reli%>%filter(type == "recipient")%>%pull(match)`% ($\kappa$ = `r reli%>%filter(type == "recipient")%>%pull(kappa)`), for speech acts it was `r reli%>%filter(type == "speechact")%>%pull(match)`% ($\kappa$ = `r reli%>%filter(type == "speechact")%>%pull(kappa)`) and for gestures it was `r reli%>%filter(type == "gesture")%>%pull(match)`% ($\kappa$ = `r reli%>%filter(type == "gesture")%>%pull(kappa)`). To get inter-rater reliability for the coding of themes, we asked whether the two coders agreed on whether a given utterance belonged to the same theme as the previous utterance or belonged to a new theme. Once again, agreement between coders was high (agreement = `r reli%>%filter(type == "theme")%>%pull(match)`%, $\kappa$ = `r reli%>%filter(type == "theme")%>%pull(kappa)`).

@@

For each of the research questions (see below), we defined a response variable and then used Bayesian multilevel regression models to model the effect of cultural setting and -- whenever applicable -- that of the different individuals involved in the conversation. To make inferences about the importance of predictors, we compared a set of nested models including cultural setting and individual as predictors to each other and to a null model that did not include them to test if these predictors improved model fit. Following @mcelreath2018statistical, we compared models using Widely Applicable Information Criteria (WAIC) and the corresponding weights. This approach favors models that have high out-of-sample predictive accuracy in that they achieve a good fit to the data with the minimal set of parameters.

We modeled the effect of cultural settings as random effects and interactions between additional variables (e.g., speaker identity) and setting as random slopes within cultural setting (`brms` notation: `(variable|setting)`). This approach partially pools model estimates and is thought to yield more generalizable results because it avoids overfitting the model to the observed data [@gelman2006data; @mcelreath2018statistical]. For each model comparison, we visualized the predictions of the winning model and interpreted them based on their posterior means and 95% Credible Intervals (CrI).

@@

```{r}
# post_silence <-silence_data%>%
#   distinct(country)%>%
#   add_epred_draws(bm1_1, re_formula =~(1|country))
# 
# p_silence <- ggplot(post_silence, aes(x = .epred, y = country))+
#   geom_point(data = silence_data, aes(x = silence, y = country),pch = 1,alpha = .5)+
#   stat_halfeye(alpha = .75, .width = c(0.66, 0.95),)+
#   xlim(0,10)+
#   labs(x = "Silence in minutes", y = "")+
#   theme_bw()
```

First, we ask how much time families spent talking as opposed to being silent and how this varied across cultural settings. The dependent variable in this case was the total lengths of all sections coded as silence for each family (modeled as a normal distribution). We compared a null model including only an overall intercept (`silence ~ 1`) to a model including cultural setting (`silence ~ 1 + (1|setting)`).

>>>>

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "manuel_bohn@eva.mpg.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal Analysis
      - Visualization
      - Writing – original draft
      - Writing – review & editing
  - name          : "Wilson Filipe da Silva Vieira"
    affiliation   : "2"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Marta Giner Torréns"
    affiliation   : "3"
    role:
      - Investigation
      - Conceptualization
      - Methodology
      - Writing – review & editing
  - name          : "Joscha Kärtner"
    affiliation   : "3"
    role:
      - Investigation
      - Conceptualization
      - Methodology
      - Writing – review & editing
  - name          : "Shoji Itakura"
    affiliation   : "4"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Lília Cavalcante"
    affiliation   : "5"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Daniel Haun"
    affiliation   : "2"
    role:
      - Investigation
      - Writing – review & editing
  - name          : "Moritz Köster"
    affiliation   : "6,*"
    role:
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing
  - name          : "Patricia Kanngiesser"
    affiliation   : "7,*"
    role:
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Institute of Psychology, Leuphana University Lüneburg, Lüneburg, Germany"
  - id            : "2"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "3"
    institution   : "Department of Psychology, University of Münster, Münster, Germany"
  - id            : "4"
    institution   : "Center for Baby Science, Doshisha University, Kyoto, Japan"
  - id            : "5"
    institution   : "Graduate Program in Theory and Research of Behavior, Federal University of Pará, Belém, Brazil"
  - id            : "6"
    institution   : "Institute of Psychology, University of Regensburg, Regensburg, Germany"
  - id            : "7"
    institution   : "School of Psychology, University of Plymouth, Plymouth, UK"
  - id            : "*"
    institution   : "joint senior authors"

authornote: |
  This research was funded by a grant from Volkswagen Foundation (89611–2), awarded to P.K.. The data assessment in Kyoto was partly funded by a JSPS Fellowship to M.K.. M.B. was supported by a Jacobs Foundation Research Fellowship. We would like to thank all the research assistants who supported the data assessments and coding: Phileas Heim, Chisato Fukuda, Julia Ohlendorf, Marlene Abromeit. We are grateful to Luke Maurits for statistical advice. All data and analysis code can be found in the following repository: https://github.com/ccp-eva/mealtime.

abstract: |
  Children all over the world learn language, yet, the contexts in which they do so varies substantially. This variation needs to be systematically quantified to build robust and generalizable theories of language acquisition. We compared communicative interactions between parents and their two-year-old children (N = 99 families) during mealtime across five cultural settings (Brazil, Ecuador, Argentina, Germany, Japan) and coded the amount of talk and gestures as well as their conversational embedding (interlocutors, function, themes). We found a comparable pattern of communicative interactions across cultural settings, which were modified in ways that are consistent with local norms and values. These results suggest that children encounter similarly structured communicative environments across diverse cultural contexts and will inform theories of language learning.

keywords          : "Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction"
wordcount         : "8454"

@@

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no

@@

Cultural norms and beliefs structure social interactions and communication. As a consequence, children learn language under very different circumstances. We studied communicative interactions between parents and their children in five diverse cultural contexts. We found a common, child-centered pattern of communication that was modified in line with local norms and values. This suggests that children can rely on similar information sources and learning processes across cultural contexts.

@@

In recent decades, research on language acquisition has focused, to a large extent, on variation in language input and, in particular, the number of words children hear in naturalistic settings. This line of work was sparked by the finding that children who receive more input -- especially speech directly addressing them -- have larger vocabularies [@hart1995meaningful; @weisleder2013talking; @bang2022spanish; @huttenlocher1991early; @walker1994prediction; @shneidman2012language]. From a theoretical perspective, more language input increases children’s opportunities for learning word-meaning mappings and allows them to build a larger vocabulary [@mcmurray2012word; @kachergis2022toward; @jones2017diversity]. The introduction of daylong audio recording devices and automated coding algorithms has provided further momentum to this endeavor [@lavechin2020open; @greenwood2011assessing; @cristia2021thorough]. As a consequence, the quantity of direct language input plays a central role in theories and formal models of language learning [@swingley2018quantitative; @braginsky2019consistency; @goodman2008does; @kachergis2022toward].

However, like most of developmental psychology [@nielsen2017persistent; @amir2020cross], research on language acquisition has largely focused on affluent societies of the Global North and the resulting theoretical proposals may fail to generalize to other cultural contexts. As studies in a greater variety of cultural settings have begun to accumulate [@casillas2021early; @bergelson2019north; @bunce2020cross; @loukatou2021child; @cristia2019child; @altinkamics2014context; @choi2000caregiver; @tardif1997caregiver], they have revealed substantial cultural variation in how much direct input children receive [@cristia2022systematic; see also @sperry2019reexamining for variation within an English-speaking sample]. Yet, children still reach major milestones in language development at similar ages [@casillas2020early; @brown2014language]. These findings highlight that theories and models of language learning need to extend beyond quantity of input and also include learning processes that compensate for variation in input [@kachergis2022toward; @jones2017diversity; @meylan2022learning; @bang2022time; @casillas2022learning].

It has been suggested that these compensatory learning processes leverage structural features of social interactions in which language is used [@rogoff2003firsthand; @casillas2020early; @shneidman2012language; @shneidman2016child]. Pragmatic accounts of language learning offer an explanation for how children use contextual information [e.g., @bohn2019pervasive; @tomasello2009constructing]: Social interactions, especially routines, follow predictable patterns that make it easier for children to infer what speakers are communicating about [@lieven1994crosslinguistic; @de2022ten; @masek2021beyond; @bruner1983child; @vygotsky1978mind]. For instance, @roy2015predicting found that words were more easily learned when they were primarily used in a distinct spatial and temporal context. Similarly, establishing common ground over the course of an interaction provides information about the speaker’s intention independent of the words that are being used [@bohn2018common; @bohn2021young]. For example, @bohn_le_peloquin_koymen_frank_2020 showed that children identify the referent of an ambiguous word by inferring the topic of an ongoing conversation [see also @akhtar2002relevance]. These findings help to explain why the amount of conversational turn-taking in parent-child interactions predicts child language outcomes [@romeo2018beyond; @donnelly2021longitudinal]. Turn-taking results in continuous, structured conversations that provide information-rich learning opportunities.

To assess whether children can use structural features to complement direct verbal input, it is crucial to compare communicative interactions between adults and children across cultural settings. However, to our knowledge, there are very few quantitative comparisons. While ethnographic descriptions offer important and rich insights into individual cultural settings [see e.g., @de2011language; @gaskins2006cultural], quantitative comparisons are essential for understanding gradual cultural differences [@koester2022parental; @broesch2021opportunities; @hewlett1998culture] and offer core input for theory building.

One of the challenges of cross-cultural work lies in selecting an appropriate context for comparing the structure of communicative interactions [@broesch2022roadmap]. Prior work has shown that the amount of language input children receive varies substantially across routine activities. For example, @soderstrom2013caregivers found that Canadian adults spoke most during book reading and structured playtime [see also @tamis2019routine]. Such activities, however, are very specific to industrialized societies and less frequent or absent in other cultural contexts. A cross-culturally recurrent, and hence particularly promising, context for cross-cultural research are mealtimes: across societies, meals are social events that are structured by -- and used to transmit -- cultural norms, values and beliefs [@ochs2006cultural; @fjellstrom2004mealtime; @blum2012dinner; @koester2022parental]. Furthermore, mealtimes have proven fruitful for studying caregiver-child communication in cultural contexts like the U.S. [e.g., @beals1993explanatory; @beals1997sources; @snow2006mealtime].

@@

The goal of this study was to compare communicative interactions between parents and their children during mealtimes across diverse cultural settings. We aimed for a naturalistic but comparable setup by a) asking families to record in their homes, b) recruiting families with a single -- usually the first -- child between 2 and 3 years of age and c) focusing on 10-minute-long episodes during which three family members (mother, father, one child) were present. Even though the constellation of two parents and one child might be less representative of the overall family demographics in some settings, it allowed us to directly quantify and compare communicative interactions.

We obtained recordings from five different cultural settings, including families living in the Global South and the Global North, as well as in urban and rural settings: the city of Buenos Aires  in Argentina, small villages in the Amazon region near Apeú in Brazil), small villages close to Cotacachi in Ecuador, the city of Münster in Germany, and the city of Kyoto in Japan. This sample was first and foremost a convenience sample of families in diverse cultural settings we had worked with previously. This continues to be a common approach in larger-scale cross-cultural, developmental studies [@house2013ontogeny; @house2020universal; @kanngiesser2022children; @blake2015ontogeny] and is often the first step when little substantive cross-cultural data exists to inform targeted comparisons. Nevertheless, in addition to their geographic spread and variation in population density, the settings also varied in cultural norms and beliefs about communication during mealtimes. In Germany, meals are seen as a privileged time for communication and exchange [@danesi2018cross]. Similarly, in Argentina, dinners are an important opportunity for family conversations  because it is usually the only time when the whole family gets together [@aguirre2016olla]. In contrast, within the Kichwa indigenous people in Ecuador meals are supposed to be taken in silence [@sanchez2010oficio]. In Japan, both views are common and whether or not talk is encouraged depends, in part, on the eating arrangements [@imada2020traditional]. As such, our sample provided us with the opportunity to study if and how different cultural mealtime norms impact real-world communicative interactions.

We coded and analyzed our video data along several dimensions, focusing on the quantity of talk and gestures as well as their conversational embedding . We chose dimensions that have been implicated as relevant for child language acquisition, but have rarely been studied from a cross-cultural perspective. First, we coded the presence (or absence) of speech, the identity of the speaker and the recipient. This allowed us to quantify how much directed talk – as opposed to overheard talk – children received and from whom. As noted above, cross-cultural variation in talk directed at the child has profound theoretical implications because it questions the privileged role given to direct input in many theoretical accounts of language learning. Coding speaker identity provided insight into who children receive language input from. Cross-cultural research on different sources of language input is relatively scarce: most past studies have exclusively focused on maternal talk and only recently have researchers begun to investigate paternal talk [@ferjan2022fathers]. By coding the language produced by children themselves, we were able to quantify children’s role in shaping their linguistic environment across cultural contexts [@tamis2018taking; @donnellan2020infants]. In addition to speech, we also coded the production of gestures. A substantial body of research has shown that gestures produced by children and their caregivers relate to child language competency -- at least in children growing up in the Global North [e.g., @rowe2008learning; @colonnesi2010relation]. Here, the view is that gestures act as a complementary source of input that reference objects and events in the environment and thereby facilitate word learning [@tomasello2005constructing].

Second, we coded how utterances were grouped into themes. This approach allowed us to quantify cross-cultural variation in how conversations are structured. Research on conversational turn-taking has suggested a link between these structural features and language learning [@donnelly2021longitudinal; @romeo2018beyond]; yet, a cross cultural perspective is still largely missing. Finally, we coded the function of utterances and distinguished between questions, assertions and imperatives. Questions play a role in facilitating language acquisition because they encourage verbal responses from children which may include labels for objects [@blake2006book]. There is also suggestive evidence of cultural variation in how parents use functional elements of language such as questions [@kuchirko2020say].

For the analysis, we first assessed  if and how these coded  dimensions differed in the five cultural settings. In a second step, we asked whether some cultural settings are more similar to one another. The five cultural settings offer an interesting perspective on the factors influencing mealtime conversations. For example, communicative interaction patterns could cluster by country (five clusters; one cluster per country), or by language family and geographical region (three clusters; Argentina, Brazil, Ecuador vs. Germany vs. Japan) or by degree of urbanization (two clusters; urban: Argentina, Germany, Japan vs. rural: Brazil, Ecuador). Based on previous work, we expected less direct input to children in the rural contexts [@cristia2022systematic]. Due to different cultural norms around mealtime conversations, we predicted less overall talk in Ecuador compared to Germany, with Japan falling somewhere in the middle.  Given a lack of comparable previous work -- we had no specific predictions for variation in the structure of communicative interactions.

@@

The final sample consisted of `r sum(dem$n)` families from five cultural contexts. This included `r dem%>%filter(country == "Argentina")%>%pull(n)` families from the city of Buenos Aires, Argentina (urban setting), `r dem%>%filter(country == "Brazil")%>%pull(n)` families from villages in the Amazon region near Apeú, Brazil (rural setting), `r dem%>%filter(country == "Ecuador")%>%pull(n)` from villages near Cotacachi, Ecuador (rural setting), `r dem%>%filter(country == "Germany")%>%pull(n)` families from the city of Münster, Germany (urban setting) and `r dem%>%filter(country == "Japan")%>%pull(n)` families from the city of Kyoto, Japan (urban setting). For the recording sessions, all families comprised a father, a mother and a child aged between 2 years and 3 years, 2 months. Almost all children were the first child in the family. Some videos partly included additional children (n = 1 for Argentina, Brazil and Ecuador, respectively).

@@

Families lived in villages of around 50 - 300 families in the Amazon region near Apeú, approximately 1.5 hours east of Belém, the capital of the state of Pará. They were recruited with the help of a local public health office. The family language was Brazilian Portuguese. Compensation included small toys for children and a certificate of participation for parents. Most parents had completed secondary school (~12 years of schooling, mothers: 50%; fathers: 56%). Mothers worked mainly as housewives (83%) while fathers engaged in paid labor (100%). Some families engaged in traditional subsistence activities such as tapioca farming, livestock breeding, or açaí and fruit harvesting. In line with employment status, the majority of children were looked after by their mothers.

@@

Here we coded who produced the utterance. The speaker could either be `child`, `mother`, or `father`. All sections containing no speech were coded as `non-talk`.

@@

### Themes and utterances

Here we coded the conversational coherence of the different utterances. For that we defined `themes` as sequences of utterances that related to one another. This applies for example to sequences of questions and answers but also to sequences in which the content of an utterance is directly related to the content of the previous utterance. Please note that such themes were coded locally and were not the same as topics. For example, if father and child exchanged four utterances about the child’s day in the kindergarten this was coded as one theme. If the same topic (day at the kindergarten) came up later again, this was coded as a separate theme. Each utterance within a theme was counted to capture the sequence and length of a theme. Thus, each utterance was assigned a number for the theme and a number for the utterance within the theme. Themes could have interjections of one or two utterances. After more than two interjections we coded a new theme. For example, if father and child talked about food and the mother made an unrelated comment in between, the mother’s comment would be coded as a separate theme while the other theme continued around it:

Child: "I want more"	 			        (theme (t) 1, utterance (u) 1)

Father: "Do you want more soup?"		(t1, u2)

Mother: "Phew, I'm hot			        (t2, u1)

Child: "No, bread				            (t1, u3)

Father: "I'll get some"			        (t1, u4)

### Functional elements

Each utterance was coded as either being a `question`, `assertion` or `imperative`. Imperatives were only coded if the utterance was grammatically structured as an imperative. For example "Pass me the salt!" was coded as an imperative while "You should give me the salt." was not.

@@

For each cultural setting, we selected 15% of videos and had them re-coded by a second coder (native speaker of the respective language). The second coder relied on the sequencing of the primary coder. Inter-rater reliability was generally very good. For recipient, the agreement between coders was `r reli%>%filter(type == "recipient")%>%pull(match)`% ($\kappa$ = `r reli%>%filter(type == "recipient")%>%pull(kappa)`), for function it was `r reli%>%filter(type == "speechact")%>%pull(match)`% ($\kappa$ = `r reli%>%filter(type == "speechact")%>%pull(kappa)`) and for gestures it was `r reli%>%filter(type == "gesture")%>%pull(match)`% ($\kappa$ = `r reli%>%filter(type == "gesture")%>%pull(kappa)`). To get inter-rater reliability for the coding of themes, we asked whether the two coders agreed on whether a given utterance belonged to the same theme as the previous utterance or belonged to a new theme. Once again, agreement between coders was high (agreement = `r reli%>%filter(type == "theme")%>%pull(match)`%, $\kappa$ = `r reli%>%filter(type == "theme")%>%pull(kappa)`).

@@

For each of the research questions (see below), we defined a response variable and then used Bayesian multilevel regression models to model the effect of cultural setting and -- whenever applicable -- that of the different individuals involved in the conversation. To make inferences about the importance of predictors, we compared a set of nested models including cultural setting and individual as predictors to each other and to a null model that did not include them to test if these predictors improved model fit. Following @mcelreath2018statistical, we compared models using Widely Applicable Information Criteria (WAIC). This approach favors models that have high out-of-sample predictive accuracy in that they achieve a good fit to the data with the minimal set of parameters.

We modeled the effect of cultural settings as random effects and interactions between additional variables (e.g., speaker identity) and setting as random slopes within cultural setting (`brms` notation: `(variable|setting)`). This approach partially pools model estimates and is thought to yield more generalizable results because it avoids overfitting the model to the observed data [@gelman2006data; @mcelreath2018statistical]. For each model comparison, we report the difference in WAIC estimates, the standard error of the difference and the weight of each model. Model weights give the probability that a model will make the best predictions out of all the models considered.

Each model comparison has a "winning" model, that is, a model that has the lowest WAIC value and the highest weight and thus, the highest expected out-of-sample predictive accuracy. However, two models can be more or less equivalent when the difference in WAIC is small and the standard error of the difference is larger than the difference in WAIC. In addition to the model comparison, we visualize the predictions of the winning model and interpret them based on their posterior means and 95% Credible Intervals (CrI).

@@

```{r}
# post_silence <-silence_data%>%
#   distinct(country)%>%
#   add_epred_draws(bm1_1, re_formula =~(1|country))
# 
# p_silence <- ggplot(post_silence, aes(x = .epred, y = country))+
#   geom_point(data = silence_data, aes(x = silence, y = country),pch = 1,alpha = .5)+
#   stat_halfeye(alpha = .75, .width = c(0.66, 0.95),)+
#   xlim(0,10)+
#   labs(x = "Non-talk in minutes", y = "")+
#   theme_bw()
```

First, we ask how much time families spent talking as opposed to not talking and how this varied across cultural settings. The dependent variable in this case was the total lengths of all sections coded as non-talk for each family (modeled as a normal distribution). We compared a null model including only an overall intercept (`non-talk ~ 1`) to a model including cultural setting (`non-talk ~ 1 + (1|setting)`)^[One might suspect that the child’s age influences their own behavior or that of the parents. To explore this possibility, we added models including child age as a predictor to the model comparison for the first three models (overall talk, talk per speaker and talk received by each individual). The inclusion of age did not improve the fit of the otherwise best fitting model any further. In the interest of space and readability, we do not report these models here. However, age is included in the data set available in the associated repository so interested readers can further explore the relation between age and the variables we coded.
].

The model comparison clearly favored the model including cultural setting (WAIC = `r comp_silence%>%filter(model == "bm1_1")%>%pull(waic)`, se = `r comp_silence%>%filter(model == "bm1_1")%>%pull(se_waic)`, weight > 0.99) over the null model (WAIC = `r comp_silence%>%filter(model == "bm1_0")%>%pull(waic)`, se = `r comp_silence%>%filter(model == "bm1_0")%>%pull(se_waic)`, weight < 0.01). The difference in WAIC (dWAIC) was = `r comp_silence%>%filter(model == "bm1_0")%>%pull(elpd_diff)` with a standard error of `r comp_silence%>%filter(model == "bm1_0")%>%pull(se_diff)`. The model predicted an average of `r fix_b1_1%>%pull(Estimate)` [95%CrI = `r fix_b1_1%>%pull(Q2.5)` - `r fix_b1_1%>%pull(Q97.5)`] minutes of non-talk across cultural settings. Ecuador and Brazil had longer sections of non-talk compared to Argentina and Germany, with Japan falling in the middle (see Figure \@ref(fig:fig1)A).
